Nondeterministic Bigraphical Reactive Systems for Markov Decision Processes\thanks{Supported by an EPSRC Vacation Scholarship.}

### 2018-08-23 paper.tex
Presentation: animations

\lstinputlisting[caption={The initial map: three consecutive cells, the midmost
of which has an inner room.}, captionpos=b, language=Big, label=agent2_initial,
firstline=15, lastline=19]{models/agent2/agent.big}

@@

\lstinputlisting[caption={Two ways to generate a room, leaving one door either
open or closed.}, captionpos=b, language=Big, label=agent2_room,
firstline=21, lastline=48]{models/agent2/agent.big}

\lstinputlisting[caption={The action of going north.}, captionpos=b,
language=Big, label=agent2_north, firstline=66,
lastline=75]{models/agent2/agent.big}

>>>>

\lstinputlisting[caption={The initial map: three consecutive cells, the midmost
of which has an inner room.}, captionpos=b, language=Big, label=agent2_initial,
firstline=16, lastline=20]{models/agent2/agent.big}

@@

\lstinputlisting[caption={Two ways to generate a room, leaving one door either
open or closed.}, captionpos=b, language=Big, label=agent2_room,
firstline=22, lastline=49]{models/agent2/agent.big}

\lstinputlisting[caption={The action of going north.}, captionpos=b,
language=Big, label=agent2_north, firstline=67,
lastline=76]{models/agent2/agent.big}
